PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-01-19 main.tex
Add figures for section 6

\subsection{Planetesimal Size and Extent of Hill Sphere}

@@

\section{Assembly History of Embryos}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/smooth_frac.png}
    \caption{Caption goes here.\label{fig:smooth_frac}}
\end{center}
\end{figure}

Show planetesimal distribution for each embryo, will look at this in more detail in paper 2

Show smooth vs chunky accretion plot for each embryo. Boundary visible at 60d

@@

@@

@@

>>>>

\subsection{Planetesimal Size and Extent of Hill Sphere}\label{sec:sizeandhill}

@@

\subsection{Assembly History of Embryos}\label{sec:assembly}

Further insight into the difference between the short vs long period accretion modes can be gained by examining the merger history of the planetary embryos. Because all collisions are directly resolved by the N-body code, a direct lineage can be traced between each embryo and a set of initial planetesimals.

We begin by investigating the `smoothness' of the accretion events that give rise to each embryo. Drawing from a common technique used for cosmological simulations (citation?), we divide growth events for a given body into `major' and `minor' mergers. Minor events are defined as any collision involving an initial planetesimal, while major events consist of any two larger bodies. In figure \ref{fig:minor_frac}, we show the total mass fraction gained by minor events as a function of mass for the 100 largest bodies at the end of fdHi. Blue dots represent bodies interior to the 60 day orbital period boundary, while red crosses indicate bodies exterior. For the outer bodies in the oligarchic growth region, we see a very weak trend between minor accretion mass fraction and total mass. Regardless of how much an embryo has grown, the initial mass planetesimals contribute about the same relative amount to its total mass. At shorter orbital periods, however, there is a somewhat stronger trend. The largest bodies in this region gain about an order of magnitude more of their mass fraction from major mergers, compared to the smallest bodies.

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/minor_frac.png}
    \caption{Caption goes here.\label{fig:minor_frac}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/acc_zones.png}
    \caption{Caption goes here.\label{fig:acc_zones}}
\end{center}
\end{figure}

The difference in slope of the short vs longer period bodies in figure \ref{fig:minor_frac} indicates a difference in how the planetesimal-embryo populations interact in each region. In the long period oligarchic growth region, embryos continue to accrete planetesimals as they grow and the minor mass fraction stays mostly flat. At short period, collisions mostly occur between equal mass bodies as the embryos grow and the contribution from planetesimals becomes less significant over time. This suggests that embryo-embryo collisions are common at short period. As discussed in section \ref{sec:sizeandhill}, the importance of gravitational scattering is greatly reduced here. Without frequent gravitational interactions between the embryos and planetesimals, orbital repulsion \citep{kokubo98} and isolation of the embryos does not occur. As we showed in figure \ref{fig:surfden_iso}, the embryos formed in this region exceed the isolation mass.

Further evidence for the lack of gravitational scattering events can be seen in figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive bodies from the fdHi simulation and arranged them in order of present orbital period. The vertical black line indicates the orbital period of each embryo. The associated histogram for each body denotes where the planetesimals used to construct that embryo originated in the disk. The peaks of the histograms have all been normalized to the same value, so that the distributions only show the relative widths and locations of the feeding zones. Beyond the 60 day boundary, the ordering of the feeding zones and the embryo locations become much less consistent. This suggests that scattering events between embryos are much more common beyond this accretion mode boundary. In the inner region of the disk, close encounters between embryos often result in a merger, which allows them to grow beyond the isolation mass while only a minor alteration to their orbital period. With few close encounters resulting in a scattering event, embryos are unable to move away from their birth location.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/f6f4.png}
    \caption{Caption goes here.\label{fig:f6f4}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/frag_ecc.png}
    \caption{Caption goes here.\label{fig:frag_ecc}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/frag_evo.png}
    \caption{Caption goes here.\label{fig:frag_evo}}
\end{center}
\end{figure}

@@

\subsection{Type I Migration}
